PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd

>>>>

```{r coping ocir base sum score if missigng items set to NA}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    ocir.sum_score_base =
      if_else(condition = na_per_person_ocir_base > 0,
              true = NA_real_,
              false = ocir.sum_score_base_raw,
              missing = NA_real_
      )
  )

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw, stats = "common")

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base, stats = "common")
```

```{r coping ocir retro sum score if missigng items set to NA}
coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
  mutate(
    ocir.sum_score_retro =
      if_else(condition = na_per_person_ocir_retro > 0,
              true = NA_real_,
              false = ocir.sum_score_retro_raw,
              missing = NA_real_
      )
  )

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw, stats = "common")

coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro, stats = "common")
```
